---
title: "Expandable Sections Example"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    self_contained: true
    number_sections: true
    toc_depth: 3
    df_print: "paged"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Section 1: Introduction

<details open>
  <summary>Click to expand</summary>
  
  This section provides an introduction to the document. It contains background information and context.

</details>

# Section 2: Data Analysis

<details>
  <summary>Click to expand</summary>
  
  This section covers the data analysis performed, including methods, tools, and results.

  ```{r analysis}
  # Sample R code for data analysis
  summary(cars)
  ```

</details>

# Section 3: Results

<details>
  <summary>Click to expand</summary>
  
  This section presents the results of the analysis. It includes tables, charts, and key findings.

  ```{r results}
  # Sample plot
  plot(cars)
  ```

</details>

# Section 4: Conclusion

<details>
  <summary>Click to expand</summary>
  
  This section summarizes the conclusions drawn from the analysis and suggests future work.

</details>
