
# Additional Information

### List of all chemicals


```{r FullChemListSetup, eval=TRUE, results='asis', echo=FALSE, message=FALSE}
###The full list of all chemicals tested can be found online at: `r makeClickableURL(URL_of_Chemicals_Tested, "MyExposome Chemical List")`
if(!is.null(URL_of_Chemicals_Tested)) {
  message<-paste0("The full list of all chemicals tested can be found online at: ",makeClickableURL(URL_of_Chemicals_Tested, "MyExposome Chemical List"))
} else {
  message <- "See supplied data files for the full list of tested chemicals"
}

cat(message)

```



```{r FullChemList, eval=FALSE, results='asis', echo=FALSE, message=FALSE}
####I'm SUPPRESSING the full list, for now, because it is LONG.  Taking first 10 rows only.
#mP<-masterParam[1:10,c("ParameterName","CASNumber")]
mP<-masterParam[1:min(nrow(masterParam),100),
                c("ParameterName","CASNumber")]
names(mP)<-c("Chemical Name", "CAS Number")
#knitr::kable(mP[1:10,],format="markdown")

pandoc.table(mP,
             caption="Full List of Chemicals",
             justify=c("left","center"),
             emphasis.rownames=TRUE,
             split.table = Inf
             )
rm(mP)

```


<br>

### Other information about report

```{r Versions,  results='asis', echo=FALSE, message=FALSE}
info <- sessionInfo()
r_ver <- paste(info$R.version$major, info$R.version$minor, sep=".")
today <- Sys.Date()

#Make a URL to insert in the text
MyExpo_URL <- makeClickableURL("http://www.myexposome.com","MyExposome, Inc.")

```


Report contents, structure, and results copyright(c) MyExposome, Inc.  All rights reserved.  Report produced on `r format(today,"%m/%d/%y")` 
<br>
This information is made available to you by `r MyExpo_URL` The Information provided is for research, informational, entertainment and educational use only. The services are not intended to be used for any diagnostic purpose and are not a substitute for medical advice. 
