
# Individual Results `r tabsetting`


## Check against Databases 

For all the chemicals found on your wristband we will look that chemical up in various databases to show what various scientific organizations have determined regarding issues with those chemicals.  Please note that unless we specificaly mention it, we do not have information that determines any of the levels reported on these compounds are unsafe.



### EPA IRIS 

Some of the chemicals found on your wristband have evaluations available from the United States Environmental Protection Agency (EPA).  The EPA's Integrated Risk Information System (IRIS) is a human health assessment program that evaluates information on health effects that may result from exposure to environmental contaminants. Through the IRIS Program, EPA provides science-based human health assessments to support the Agency's regulatory activities. The IRIS database [(http://www.epa.gov/iris/)](http://www.epa.gov/iris/) is web accessible and contains information on more than 550 chemical substances.  We have looked up all the chemicals found on your wristband and provided links to the data on the EPA IRIS web site in those cases where the data is available. 
<br>
<br>



```{r  epaIrisPrint, results='asis', echo=FALSE, message=FALSE}

pandoc.table(as.data.frame(oneResultEpaIris),
             caption="Observed Chemical List showing EPA IRIS URLs",
             justify=c("left","center"),
             emphasis.rownames=TRUE
              ,split.table = Inf)

#rm(oneResultEpaIris)
#rm(epaIris)

```



<br>
<br>



```{r   califProp65printx1, results='asis',echo=FALSE,  eval=(nrow(oneResultCalifProp65Risk)!=0) }

cat("### Proposition 65")

```

&nbsp;

```{r   califProp65printx2, results='asis',echo=FALSE,  eval=(nrow(oneResultCalifProp65Risk)!=0) }

cat("Some of the chemicals found on your wristband are classified per California Proposition 65",
      "[(http://www.oehha.ca.gov/prop65.html)](http://www.oehha.ca.gov/prop65.html)",
      "which categorizes many different chemicals with respect to toxicity (potential hazard). ",
      "Of the chemicals found on your wristband, here are the ones that are listed as",
      "having some type of toxicity per California Proposition 65. ",
      "There are four types of toxicity catagorized by Prop65:  Cancer, Developmental Toxicity, ", 
      "Female Reproductive Toxicity, and Male Reproductive Toxicity. ",
      "We have summarized some of the listed ",
      "risks in the table below but please refer to the official California website ",
      "listing specific risks for each chemical for up-to-date and accurate information:",
      "[(https://www.p65warnings.ca.gov/fact-sheets)](https://www.p65warnings.ca.gov/fact-sheets)",
      sep=" ")


```


```{r  califProp65printx3, results='asis', echo=FALSE, message=FALSE, eval=(nrow(oneResultCalifProp65Risk)!=0)}

pandoc.table(as.data.frame(oneResultCalifProp65Risk),
             caption="Observed Chemical List showing California Prop 65",
             justify=c("left","center")
              ,split.table = Inf)

#rm(oneResultCalifProp65Risk)

```

<br>
<br>



```{r   IARCprintx1, results='asis',echo=FALSE, eval=(nrow(oneResultIARCRisk)!=0)}

cat("### IARC")


```

```{r   IARCprintx2, results='asis',echo=FALSE, eval=(nrow(oneResultIARCRisk)!=0)}

cat("The chemicals found on the wristband are classified by the International Agency",
      "for the Research on Cancer [(https://monographs.iarc.who.int/agents-classified-by-the-iarc/))](https://monographs.iarc.who.int/agents-classified-by-the-iarc/))",
      "which categorizes many different chemicals with respect to types of cancer risks.",
      "Of the chemicals found on your wristband, here are the ones that are listed as having some type of rating per IARC.  ",
      sep=" ")

```


```{r   IARCprintx2a, results='asis',echo=FALSE, eval=FALSE}
"[^1]: * **IARC classifies risks into four groups:**"
cat("+ Group 1: The agent is Cancer-causing to humans:  This category is used when there is sufficient evidence of cancer causing in humans.")
cat("+ Group 2A: The agent is probably Cancer-causing to humans:  This category is used when there is limited evidence of Cancer-causing in humans and sufficient evidence of Cancer-causing in experimental animals. ")
cat("+ Group 2B: The agent is possibly Cancer-causing to humans:  This category is used for agents for which there is limited evidence of Cancer-causing in humans and less than sufficient evidence of Cancer-causing in experimental animals. ")
cat("+ Group 3: The agent is not classifiable as to its Cancer-causing to humans: This category is used most commonly for agents for which the evidence of Cancer-causing is inadequate in humans and inadequate or limited in experimental animals.  An evaluation in Group 3 is not a determination of non-carcinogenicity or overall safety. ")
cat("+ Group 4: The agent is probably not Cancer-causing to humans: This category is used for agents for which there is evidence suggesting lack of Cancer-causing in humans and in experimental animals. ")


```


```{r IARCprintx3, results='asis', echo=FALSE, eval=(nrow(oneResultIARCRisk)!=0), message=FALSE}

pandoc.table(as.data.frame(oneResultIARCRisk),
             caption="Observed Chemical List showing IRAC classification",
             justify=c("left","center")
              ,split.table = Inf)


#rm(oneResultIARCRisk)
#rm(IARCRisk)

```

<br>
<br>


## Individual: Chemical Info



```{r IndividualChemicalListWithClassification, child='IndividualChemicalListWithClassification_text.Rmd', eval = !HideClassificationInformation}
```


```{r IndividualChemicalListWithOutClassification, child='IndividualChemicalListWithOutClassification_text.Rmd', eval = HideClassificationInformation}
```



```{r IndividualClassificationShowingChemicalsAndAverages, child='IndividualClassificationShowingChemicalsAndAverages_text.Rmd', eval = !HideClassificationInformation}
```





### Individual Percentage vs Maximum 


Another way to look at this is to wonder what percentage of a chemical a particular individual had compared to the maximum found for that chemical in any wristband in this project.   In other words, if wristband-A had 100 nano-grams per gram of wristband, and the maximum found in any individual was 1,000 nano-grams per gram wristband, then wristband-A had 10% of the maximum value found. The chart below shows the percentage of maximum found for this subject for each chemical.

`r if(nrow(testResults.big[testResults.big[, "Flag"] == "Y", ])>0){"Any wristbands where we detected a chemical, but could not quantify it, are suppressed from this chart below"}`


```{r chart_x5_perc_values, echo=FALSE, message=FALSE, fig.height=6,fig.cap="",dpi=150}
################BEGIN x5 Perc

perc_values <- testResults.big %>%   # NOTE using TR instead of testResults just cause then it has ParameterName
  filter(SampleNumber==subject) %>%
  select(ParameterName,norm_Result) 

 c<-ggplot(perc_values, aes(y=norm_Result ,factor(ParameterName))) +
    #geom_bar(stat="identity")+
    geom_bar(stat="identity", fill="blue", colour="black")+
    labs(x="All Chemicals Found for Anyone",
         y="Percent of Max value Found",
         title=paste("Your Percentage of Max Exposure\n",
                     "Found per Chemical\n",
                     "Subject = ",subject))
#c

axis.text.x.size <-6  # JUST changed to be a variable
if (howManyUniqueChemFoundAcrossAllWristbands < 60 ) axis.text.x.size <-10
c<- c+theme(axis.line=element_blank(),
            axis.ticks=element_blank(),
            axis.title.x=element_blank(),
           axis.text.x = element_text(angle = 90, vjust=.1,hjust=1,size=axis.text.x.size ),
#           axis.text.x = element_text(angle = 45,vjust=1,hjust=1,size=6 ),

            legend.position="none",
            panel.background=element_blank(),
            panel.border=element_blank(),
            panel.grid.major=element_blank(),
            panel.grid.minor=element_blank(),
            plot.background=element_blank())

#c <- c + scale_y_continuous(labels=percent, limits=c(0,1))
c <- c + scale_y_continuous(labels=percent)
c

rm(c,perc_values)

```

<br>
<br>

