
### Classifications showing Chemicals

While the above table shows all the chemicals, and every classification for each chemical, this information can sometimes more easily be understood by seeing that same data organized by classification.  This allows you to see all the chemicals of a particular "type" grouped together (remembering that some chemical compounds are repeated in multiple categories).  The following list of classifications, along with their chemicals, were found in your wristband:


<!-- 
[standard deviation](## "Standard deviation is blah blah.") 
-->


```{r  ListClassFound, results='asis', echo=FALSE, message=FALSE}

oneResultInvertClassified<- as.data.frame(
  inner_join(oneResult_with_Y_flag,class_L,by="ParameterID") %>% 
    select(classification,ParameterName) %>%
    group_by(classification) %>%
    dplyr::summarise(ParameterNames=paste(ParameterName,collapse=", ")) %>%
    ungroup %>%
    mutate_if(is.factor, as.character) %>%  #Eliminate classification as a FACTOR so it sorts correctly
    arrange(classification))

names(oneResultInvertClassified)<-c("Classification", "Chemical Name(s)" )



classExplainTable <- read.table(class_explain_table_name,  sep = ",",  header = TRUE   )

### NOTE INFO:---  Making this tooltip was TRICKY... if we want to change it just get rid of it... not worth the time
### NOTE INFO:---  Making this tooltip was TRICKY... if we want to change it just get rid of it... not worth the time


# Create tooltips for each word
create_tooltip <- function(classIf) {
  class_row <- classExplainTable %>% filter(Classification == classIf)
  if (nrow(class_row) == 0) {
    return(classIf)
  }

  description <- tags$span(title = class_row$Description, "---->Description")
  sources <- tags$span(title = class_row$Sources, "---->Sources")
  examples <- tags$span(title = class_row$Examples, "---->Examples")
  strategies <- tags$span(title = class_row$Strategies, "---->Strategies")

  return(paste0(classIf, '<br>', description, '<br>', sources, '<br>', examples, '<br>', strategies))
}

# Apply the function to create tooltips
oneResultInvertClassified$Classification <- sapply(oneResultInvertClassified$Classification, create_tooltip)

#Print the table with tooltips
pandoc.table(oneResultInvertClassified,
             caption = "Classification Report on your Wristband",
             justify = c("left", "center"),
             split.table = Inf,
             emphasis.rownames = TRUE)

# knitr::kable(oneResultInvertClassified, format = "html", escape = FALSE) %>%
#  kable_styling(full_width = F)


```

### Classifications vs Averages

If we look at this same data, broken down by chemical classification, and remembering that some chemical compounds are repeated in multiple categories, we see the following.  The first numeric column is your wristband results and the second is the average of all the wristbands in this project.

`r if(nrow(testResults.big[testResults.big[, "Flag"] == "Y", ])>0){"Any wristbands where we detected a chemical, but could not quantify it, are suppressed from this chart below"}`

```{r CompareWhatClassificationsFound , results='asis', echo=FALSE, message=FALSE }

#knitr::kable(ClassCompare[,2:ncol(ClassCompare)],format="markdown")
#FIRST change column names so Partcipant becomes the actual name of the subject
# names(ClassCompareSubject)<-c("Classification",subject,"Average","maxFoundAnyOneBand")
# ClassCompareSubject<-ClassCompareSubject %>%
#     mutate_if(is.factor, as.character) %>%   #Eliminate classification as a FACTOR so it sorts correctly
#     ClassCompareSubject(Classification) 

ClassCompareSubject2 <- ClassCompareSubject %>%
    select(classification,Participant,Average) %>%
    dplyr::rename(You=Participant)


pandoc.table(ClassCompareSubject2,
              justify=c("left","center","center")
              ,split.table = Inf)

rm(ClassCompareSubject2)

```

<br>
<br>

