
### Chemical Groups showing Chemicals

While the table above shows chemicals with their groups, it may be easier to understand when the data is shown in groups instead of individual chemicals. Some chemicals may appear in more than one category.  The list below shows the groups and chemicals found on your wristband.

<!-- 
[standard deviation](## "Standard deviation is blah blah.") 
-->


```{r  ListClassFound, results='asis', echo=FALSE, message=FALSE}

oneResultInvertClassified<- as.data.frame(
  inner_join(oneResult_with_Y_flag,class_L,by="ParameterID") %>% 
    select(classification,ParameterName) %>%
    group_by(classification) %>%
    dplyr::summarise(ParameterNames=paste(ParameterName,collapse=", ")) %>%
    ungroup %>%
    mutate_if(is.factor, as.character) %>%  #Eliminate classification as a FACTOR so it sorts correctly
    arrange(classification))

names(oneResultInvertClassified)<-c("Chemical Group", "Chemical Name(s)" )



classExplainTable <- read.table(class_explain_table_name,  sep = ",",  header = TRUE   )

### NOTE INFO:---  Making this tooltip was TRICKY... if we want to change it just get rid of it... not worth the time
### NOTE INFO:---  Making this tooltip was TRICKY... if we want to change it just get rid of it... not worth the time


# Create tooltips for each word
create_tooltip <- function(classIf) {
  class_row <- classExplainTable %>% filter(Classification == classIf)
  if (nrow(class_row) == 0) {
    return(classIf)
  }

  description <- tags$span(title = class_row$Description, "---->Description")
  sources <- tags$span(title = class_row$Sources, "---->Sources")
  examples <- tags$span(title = class_row$Examples, "---->Examples")
  strategies <- tags$span(title = class_row$Strategies, "---->Strategies")

  return(paste0(classIf, '<br>', description, '<br>', sources, '<br>', examples, '<br>', strategies))
}


create_Modal_tooltip <- function(classIf) {
  class_row <- classExplainTable %>% filter(Classification == classIf)
  if (nrow(class_row) == 0) {
    return(classIf)
  }

  #bs_modal(id = "StandardDevation", title = "Standard Deviation Definition", body = "Standard deviation is a measure of how spread out the numbers in a set are from the average. A bigger standard deviation means the numbers are more spread out, while a smaller one means they're closer to the average.")
  #stdDevButton<-bs_button("standard deviation", button_type = "primary", class = "btn-xs btn-outline-info") %>% bs_attach_modal(id_modal = "StandardDevation")

  bs_modal(id = "descriptionButtonID", title = paste("Description of",classif, "chemicals"), body = class_row$Description)
  descriptionButton<-bs_button("Description", button_type = "primary", class = "btn-xs btn-outline-info") %>% bs_attach_modal(id_modal = "descriptionButtonID")

  #description <- tags$span(title = class_row$Description, "---->Description")
  sources <- tags$span(title = class_row$Sources, "---->Sources")
  examples <- tags$span(title = class_row$Examples, "---->Examples")
  strategies <- tags$span(title = class_row$Strategies, "---->Strategies")

  return(paste0(classIf, '<br>', descriptionButton, '<br>', sources, '<br>', examples, '<br>', strategies))
}



# Apply the function to create tooltips
oneResultInvertClassified$"Chemical Group" <- sapply(oneResultInvertClassified$"Chemical Group", create_tooltip)
#oneResultInvertClassified$"Chemical Group" <- sapply(oneResultInvertClassified$"Chemical Group", create_Modal_tooltip)    ### TRIED TO PUT BUTTON IN but that didn't work at all for some reason.... cause i'm paste0 in weird buttons???

#Print the table with tooltips
pandoc.table(oneResultInvertClassified,
             caption = "Chemical Group Report on your Wristband",
             justify = c("left", "center"),
             split.table = Inf,
             emphasis.rownames = TRUE)

# knitr::kable(oneResultInvertClassified, format = "html", escape = FALSE) %>%
#  kable_styling(full_width = F)


```

### Chemical Group: You vs Averages

When we break down the data by chemical groups (keeping in mind that some chemicals appear in more than one group), the results are as follows. The first column shows your wristband results, and the second column shows the average for all wristbands in this project.

`r if(nrow(testResults.big[testResults.big[, "Flag"] == "Y", ])>0){"Any wristbands where we detected a chemical, but could not quantify it, are suppressed from this chart below"}`

```{r CompareWhatClassificationsFound , results='asis', echo=FALSE, message=FALSE }

#knitr::kable(ClassCompare[,2:ncol(ClassCompare)],format="markdown")
#FIRST change column names so Partcipant becomes the actual name of the subject
# names(ClassCompareSubject)<-c("Classification",subject,"Average","maxFoundAnyOneBand")
# ClassCompareSubject<-ClassCompareSubject %>%
#     mutate_if(is.factor, as.character) %>%   #Eliminate classification as a FACTOR so it sorts correctly
#     ClassCompareSubject(Classification) 

ClassCompareSubject2 <- ClassCompareSubject %>%
    select(classification,Participant,Average) %>%
    dplyr::rename(You=Participant,"Chemical Group"=classification)


pandoc.table(ClassCompareSubject2,
              justify=c("left","center","center")
              ,split.table = Inf)

rm(ClassCompareSubject2)

```

<br>
<br>

