---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Individual Results


## Plot each Chemical of Concern {.tabset  .tabset-pills}

We checked all the chemicals you were exposed to in databases that flag harmful chemicals. Just because a chemical is flagged doesn't mean the amount you were exposed to is harmful. Also, many chemicals haven't been tested for safety so not being in a database doesn't mean it's safe. We compared your results to others in the study.  The graph shows how much of a certain chemical was found in wristbands. The blue circle is the average amount, the green circle is the middle value, and the red circle is your result. The wider pink area represents how common different amounts are, with wider parts showing levels found in more people. Click each chemical name to see how your exposure compares.

```{r PlotChemsOfConcern, results='asis',echo=FALSE,eval=TRUE}
###
### using variou web links to figure out...this is supposed to work... ineed to check this again...
###  THIS LOOKS GOOD:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops
######   THIS ONE GAVE ANSWER BELOW:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops

#plotlyC_concern <-  plotlyChems(chemsOfConcern, testResults.big, oneResultCalifProp65Risk, oneResultEpaIris, oneResultIARCRisk, chemSourceMitigation  , subject, howManyHaveParameterName, howManyWristbandsTested)
#cat(" \n about print ploty no concern\n")

# Define a Bootstrap modal POPUP for detailed health concern explanations
info_modal <- bs_modal(
  id = "info_modal",
  title = "Health Concern Information",
  body = div(
    HTML("
      <p>In the table below, <b>(FAKE INFO FOR NOW NEEDS TO BE FIXED WHEN WE DECIDE WHAT HEALTH CONCERNS TO FLAG)</b> a checkmark means there is positive evidence that the chemical exposure is linked to the health concern although the required level of exposure or length of exposure that would create a health issue is unknown. An empty box means either there is no data available, or, existing evidence does not support a link.</p>
      <ul>
        <li><strong>Reproduction and fertility:</strong> Chemicals that affect the reproductive system or people’s ability to have children.</li>
        <li><strong>Brain and behavior:</strong> Chemicals that affect the brain, nervous system, or learning and behavior.</li>
        <li><strong>Increased cancer risk:</strong> Chemicals that increase the risk of certain cancers.</li>
        <li><strong>Hormone disruption:</strong> Chemicals that interfere with your body’s natural hormones. Hormones are important for regulating nearly all your body’s systems.</li>
        <li><strong>Development:</strong> Chemicals that affect how a baby grows and develops in childhood.</li>
        <li><strong>PBT:</strong> Chemicals that are Persistent, Bioaccumulative, and Toxic. This means that they are difficult to break down and eliminate from your body and the environment.</li>
        <li><strong>Harms DNA:</strong> Chemicals that damage DNA. DNA contains all the instructions for making your body run.</li>
        <li><strong>Respiratory:</strong> Chemicals that irritate people's lungs and make asthma worse.</li>
      </ul>
    ")
  )
)


modal_trigger <- HTML("<a href='#' data-toggle='modal' data-target='#info_modal'>Click here for more information <b>Health Effects</b> in the table below</a>")
#showHealthEffectsTable <- TRUE
showHealthEffectsTable <- FALSE

if(showHealthEffectsTable){
  htmltools::tagList(
  modal_trigger,
  info_modal
) %>% htmltools::browsable()
  
}


#plotlyC_concern is a list of multiple items and for each chemical it has the TAB HEADER formatted with correct "level" so it becomes a TAB ,
#   PLUS it has the actual content of the plotly plot
#   PLUS it has the "message" that follows the plotly plot
# TODO:  Need to add something ELSE into the tab... the check-box of health concerns... and it should be printed AFTER the tab header but before the PLOT
#       so we need to create a new entry in the list for each chem that is "chemItem_healthCheckBox" or something like that
#       So when we create plotlyC... we need to add that... 
if (!is.null(plotlyC_concern)) {
  
  for (chemItem in chemsOfConcern) {
    #chemItem<-chemsOfConcern[1]

    # Print the `cat` message (tab header)
    cat(plotlyC_concern[[paste0(chemItem, "_cat_message")]], "\n")
    
    #TEST WITH:   cat(as.character(risk_table_html), "\n")
    #htmltools::browsable(plotlyC_concern[[paste0(chemItem, "_health_risk_table")]])
    #cat(as.character(plotlyC_concern[[paste0(chemItem, "_health_risk_table")]]), "\n")
    
    #cat(gt::as_raw_html(plotlyC_concern[[paste0(chemItem, "_health_risk_table")]]), "\n")

    #htmltools::HTML(as.character(plotlyC_concern[[paste0(chemItem, "_health_risk_table")]]))

    if(showHealthEffectsTable){
      cat(as.character(plotlyC_concern[[paste0(chemItem, "_health_risk_table")]]), "\n")
    }
    
    # Print the tab content
    print(plotlyC_concern[[chemItem]])
    
    # Print the explanatory message
    cat(plotlyC_concern[[paste0(chemItem, "_message")]], "\n \n")
  }
  
}



```


## Plot Remaining Chemicals {.tabset  .tabset-pills}


Besides the chemicals already mentioned, other chemicals were also found on your wristband. Many chemicals haven't been tested for safety so not being in a database doesn’t mean it’s safe, but it also doesn’t mean it’s harmful.  In fact, some of these compounds may occur naturally and even be beneficial at some levels. The graph shows how much of a certain chemical was found in wristbands. The blue circle is the average amount, the green circle is the middle value, and the red circle is your result. The wider pink area represents how common different amounts are, with wider parts showing levels found in more people. Click on each chemical name to compare your exposure to others in the study.


```{r PlotOtherChems, results='asis', echo=FALSE, eval=TRUE}
###
### using variou web links to figure out...this is supposed to work... ineed to check this again...
###  THIS LOOKS GOOD:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops
######   THIS ONE GAVE ANSWER BELOW:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops

#plotlyC_remaining <- plotlyChems(chemsNOTinConcernGroup, testResults.big, oneResultCalifProp65Risk, oneResultEpaIris, oneResultIARCRisk, chemSourceMitigation, subject, howManyHaveParameterName, howManyWristbandsTested)
#cat(" \n about print ploty \n")

#THIS VERSION BELOW WORKED EXCEPT FOR THE HEALTH RISK TABLE
# if (!is.null(plotlyC_remaining)) {
#   for (chemItem in chemsNOTinConcernGroup) {
#     # Print the `cat` message (tab header)
#     cat(plotlyC_remaining[[paste0(chemItem, "_cat_message")]], "\n")
#     
#     # Print the `healthRiskTable`
#     #print(plotlyC_concern[[paste0(chemItem, "_health_risk_table")]], "\n")
#     plotlyC_concern[[paste0(chemItem, "_health_risk_table")]]
#     
#     
#     # Print the tab content
#     print(plotlyC_remaining[[chemItem]])
#     
#     # Print the explanatory message
#     cat(plotlyC_remaining[[paste0(chemItem, "_message")]], "\n \n")
#   }
#   
#   
# }

if (!is.null(plotlyC_remaining)) {
  for (chemItem in chemsNOTinConcernGroup) {
    # Print the `cat` message (tab header)
    cat(plotlyC_remaining[[paste0(chemItem, "_cat_message")]], "\n")
    
 
    
    # Print the tab content
    print(plotlyC_remaining[[chemItem]])
    
    # Print the explanatory message
    cat(plotlyC_remaining[[paste0(chemItem, "_message")]], "\n \n")
  }
}









```



```{r StatisticsOnAllChemicalsFound, child='StatisticsOnChemicalsFound.Rmd', eval = TRUE}
```


# Chemical Group Information



```{r IndividualClassificationVsAverages, child='YourChemicalsAndAveragesByGroup_text.Rmd', eval = !HideClassificationInformation}
```


```{r IndividualChemicalListWithClassification, child='IndividualChemicalListWithClassification_text.Rmd', eval = !HideClassificationInformation}
```


```{r IndividualChemicalListWithOutClassification, child='IndividualChemicalListWithOutClassification_text.Rmd', eval = HideClassificationInformation}
```



```{r IndividualClassificationShowingChemicals, child='IndividualClassificationShowingChemicals_text.Rmd', eval = !HideClassificationInformation}
```




```{r chart_x5_perc_values, echo=FALSE, message=FALSE, fig.height=12,fig.cap="",dpi=150, eval=FALSE}




## Your Percentage vs Maximum Amount Found

<!--  THIS IS OLD LANGUAGE... improved it somewhat
Another way to view the data is by comparing how much of a chemical you had compared to the maximum found in any wristband. For example, if wristband-A had 100 nanograms and the maximum was 1,000 nanograms, wristband-A had 10% of the maximum. The chart below shows the percentage of the maximum for each chemical found on your wristband.
-->

Next we looking at the amount of each chemical you have compared to the highest amount found on anyone's wristband.  So, if the maximum amount of a certain chemical found was 1,000, and your wristband had 100, you'd have 10% of that maximum. This chart shows you that percentage for all the chemicals found on your wristband, giving you a sense of how your results stack up against the highest levels detected.

`r if(nrow(testResults.big[testResults.big[, "Flag"] == "Y", ])>0){"Any wristbands where we detected a chemical, but could not quantify it, are suppressed from this chart below"}`







################ BEGIN x5 Perc

##
perc_values <- testResults.big %>% #
  filter(SampleNumber == subject) %>%
  filter(Result > 0) %>%
  select(ParameterName, norm_Result)

c <- ggplot(perc_values, aes(y = norm_Result, factor(ParameterName))) +
  # geom_bar(stat="identity")+
  geom_bar(stat = "identity", fill = "blue", colour = "black") +
  labs(
    x = "All Chemicals Found on Your Wristband",
    y = "Percent of Max value Found",
    title = paste(
      "Your Percentage of Max Exposure\n",
      "Found per Chemical\n" # ,
      # "Subject = ", subject
    )
  )
# c

axis.text.x.size <- 6 # JUST changed to be a variable
if (howManyUniqueChemFoundAcrossAllWristbands < 60) axis.text.x.size <- 10
c <- c + theme(
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 90, vjust = .1, hjust = 1, size = axis.text.x.size),
  #           axis.text.x = element_text(angle = 45,vjust=1,hjust=1,size=6 ),

  legend.position = "none",
  panel.background = element_blank(),
  panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  plot.background = element_blank()
)

# c <- c + scale_y_continuous(labels=percent, limits=c(0,1))
c <- c + scale_y_continuous(labels = percent)
c + coord_flip()


rm(c, perc_values)
```

<br>
<br>
