---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Individual Results


```{r IRiS_Prop65_IARC_Individual_Results_COMBINED_NEW, results='asis', echo=FALSE, message=FALSE, fig.width=6, fig.height=8,fig.cap="",dpi=150,eval=DoSpecificSubjectAnalysis}
## The function to build a violin plot is now in a separate R file
#source("BuildViolinPlot.R")
source(setRdirectory("BuildViolinPlot.R"))


# Make list of all chemicals that our ONE user had that showed up in "any" of the databases
##  NOTE: I really should do this with ParameterName but didn't have that  handy... should fix
#

# chemsOfConcern <- (union(union(oneResultCalifProp65Risk$`Chemical Name`,oneResultEpaIris$`Chemical Name`),
#      oneResultIARCRisk$`Chemical Name`))
#
### ONLY DOING PROP65 and EPA IRIS... dropping IARC cause not as interseting?
chemsOfConcern <- union(oneResultCalifProp65Risk$`Chemical Name`, oneResultEpaIris$`Chemical Name`)


## Make a list of all chemicals that our one user had that did NOT show up in any of the databases
chemsNOTinConcernGroup <- oneResult_with_Y_flag$ParameterName[!(oneResult_with_Y_flag$ParameterName %in% chemsOfConcern)]
```


```{r setupViolinVariablesAndFunctions, include=FALSE}
# THIS weird few LINES is not really important except somehow by ploting, but not including (include=FALSE) this enables the rest to work?
# fig <- ggplot(cars) +
# geom_point(aes(speed, dist))
# htmltools::tagList(ggplotly(fig))
# Initialize Plotly without rendering a dummy plot
plotly::config(plot_ly(), displayModeBar = FALSE)


### This next section is to figure how HOW MANY people HAD this compound and how many didn't
howManyHaveParameterName <- testResults.big %>%
  group_by(ParameterName) %>%
  summarise(non_zero_count = sum(Result != 0))


# Function to look up non_zero_count for a specific ParameterName
lookup_non_zero_count <- function(parameter_name, howManyHaveParameterName) {
  result <- howManyHaveParameterName %>%
    filter(ParameterName == parameter_name) %>%
    pull(non_zero_count)
  return(result)
}

# Example usage
# parameter_name_to_lookup <- "Trans-Nonachlor"  # Replace with your ParameterID
# non_zero_count_value <- lookup_non_zero_count(parameter_name_to_lookup, howManyHaveParameterName)
# print(non_zero_count_value)

###  THIS LOOKS GOOD:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops
######   THIS ONE GAVE ANSWER BELOW:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops

### Extracted function below as generic way to do tabset PLOTLY of interact plots
###     NOTE that we do with set that IS listed in certain DB and set that ISN"T but ...that is an artifical split we could just collapse them
###     NOTE that in both cases we have the CODE to print the listing in those database... BUT.... it never gets hit if it's not there!

plotlyChems <- function(chemsList, testResults.big, oneResultCalifProp65Risk, oneResultEpaIris, oneResultIARCRisk, chemSourceMitigation) {
  # chemsList<- chemsOfConcern
  if (length(chemsList) >= 1) {
    for (i in 1:length(chemsList)) {
      chemItem <- chemsList[i]
      # chemItem <- chemsList[2]
  

      # NOW make a table of all the users that had the one chemical of concern that we selected which our one user had
      testResults_ChemItem <- testResults.big %>%
        filter(ParameterName == chemItem) %>%
        select(SampleNumber, Result, ParameterName)


      if(nrow(testResults_ChemItem[testResults_ChemItem$Result >0,])>1)
        {                     # THIS is hopefully skipping tring to plot any chems where only 1 ahs values
        #if (nrow(testResults_ChemItem) > 1) {
        cat("###", chemItem, "{-}", "\n\n")
        htmlTagList<- htmltools::tagList(
          buildPlotlyViolin(chemItem, testResults_ChemItem,subject)
        )

        
        if (!is.null(htmlTagList)) { 
          print(htmlTagList)
          }

        newMessage <- NULL

        newMessage <- paste(
          newMessage,
          " ",
          chemItem,
          " was found on ",
          lookup_non_zero_count(chemItem, howManyHaveParameterName),
          "out of the ",
          howManyWristbandsTested,
          "wristbands."
        )

        testInPROP65 <- oneResultCalifProp65Risk %>%
          filter(`Chemical Name` == chemItem)
        if (nrow(testInPROP65) > 0) {
          PROP65_info <- str_trim(testInPROP65$`Risk Type Per California Prop 65`)


          Prop65_Link <- "http://www.oehha.ca.gov/prop65.html"
          Prop65_Link <- makeClickableURL(Prop65_Link, "California Proposition 65")


          newMessage <- paste(
            newMessage,
            " ",
            " This chemical is classified per ",
            Prop65_Link,
            # " ) ",
            " with the risk type noted as: ",
            PROP65_info,
            "."
          )
        }

        ##### DELETED IARC cause Silent Spring suggested gettign rid
        # testInIARC <- oneResultIARCRisk %>%
        #   filter(`Chemical Name` == chemItem)
        #  if (nrow(testInIARC) > 0) {
        #    IARC_info <- testInIARC$`Risk Type Per IARC`
        #    newMessage <- paste (newMessage,  " ",
        #                         " This chemical is classified by the International Agency for the Research on Cancer ",
        #                         " as a chemical of concern.  It is classified as: ",  IARC_info,".")
        #  }

        testInIRIS <- oneResultEpaIris %>%
          filter(`Chemical Name` == chemItem)
        if (nrow(testInIRIS) > 0) {
          IRIS_info <- testInIRIS$`IRIS Summary Web Link`
          IRIS_info <- makeClickableURL(IRIS_info, "chemical of interest")

          newMessage <- paste(
            newMessage,
            " ",
            "The Environmental Protection Agency has classified this chemical as a ",
            IRIS_info,
            ". "
          )
        }

        testInChemSourceMitigation <- chemSourceMitigation %>%
          filter(Chemical_Name == chemItem)
        chemSourceMitigationMessage <- "\n\n"
        if (nrow(testInChemSourceMitigation) > 0) {
          chemSourceMitigationMessage <- paste0(
            chemSourceMitigationMessage,
            # "This compound is suspected of having the following health effects: **",         ### WE DELETED MENTION OF HEALTH EFFECTS BUT CODE STILL HERE TO PRINT IF WE UNCOMMENT THIS
            #          testInChemSourceMitigation$Summary_of_Health_Effects,
            #          "**. ",
            " Sources of Exposure to this compound:  **",
            testInChemSourceMitigation$Sources_of_Exposure,
            # testInChemSourceMitigation$Commercial_Products  This was from the first try, SOURCES of exposure seems like better data
            "**. ",
            "\n Possible ways to avoid exposure to this compound include: **",
            testInChemSourceMitigation$Mitigation_Strategies,
            "**."
          )
          if (!is.na(testInChemSourceMitigation$WIKIPEDIA_ARTICLE_URL)) {
            wikiURL <- testInChemSourceMitigation$WIKIPEDIA_ARTICLE_URL
            # wikiURL <- paste0("<a href='", wikiURL, "' target='_blank'>", wikiURL, "</a>") ## This should make the link open in new tab
            wikiURL <- makeClickableURL(wikiURL, "Wiki")
            wikiMessage <- paste0("\n Additional information: ", wikiURL)
            chemSourceMitigationMessage <- paste0(chemSourceMitigationMessage, " ", wikiMessage, "\n")
          }

          newMessage <- paste(newMessage, " ", chemSourceMitigationMessage)
        }
       # cat("\n\n about to print if( !is.null(newMessage)) {cat(newMessage)} ")
        if( !is.null(newMessage)) {cat(newMessage)}
      #  cat("\n\n just print if( !is.null(newMessage)) {cat(newMessage)} ")
        cat(" \n \n")
      }
    }
  } else {
     #cat("\n\n about to NEVERY MATC ")

    testResults_ChemItem <- testResults.big %>%
      filter(ParameterName == "NEVER MATCH") %>%
      select(SampleNumber, Result, ParameterName)
    #cat("\n\n just did  to NEVERY MATC ")

  }
}

```


## Plot each Chemical of Concern {.tabset  .tabset-pills}

We checked all the chemicals you were exposed to in databases that flag harmful chemicals. Just because a chemical is flagged doesn't mean the amount you were exposed to is harmful. Also, many chemicals haven't been tested for safety so not being in a database doesn't mean it's safe. We compared your results to others in the study.  The graph shows how much of a certain chemical was found in wristbands. The blue circle is the average amount, the green circle is the middle value, and the red circle is your result. The wider pink area represents how common different amounts are, with wider parts showing levels found in more people. Click each chemical name to see how your exposure compares.

```{r PlotChemsOfConcern, results='asis',echo=FALSE,eval=TRUE}
###
### using variou web links to figure out...this is supposed to work... ineed to check this again...
###  THIS LOOKS GOOD:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops
######   THIS ONE GAVE ANSWER BELOW:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops

plotlyC <- plotlyChems(chemsOfConcern, testResults.big, oneResultCalifProp65Risk, oneResultEpaIris, oneResultIARCRisk, chemSourceMitigation)
#cat(" \n about print ploty \n")

if (!is.null(plotlyC)) {
  print(plotlyC)
}
#cat(" \n Just print ploty \n")


```


## Plot Remaining Chemicals {.tabset  .tabset-pills}


Besides the chemicals already mentioned, other chemicals were also found on your wristband. Many chemicals haven't been tested for safety so not being in a database doesn’t mean it’s safe, but it also doesn’t mean it’s harmful.  In fact, some of these compounds may occur naturally and even be beneficial at some levels. The graph shows how much of a certain chemical was found in wristbands. The blue circle is the average amount, the green circle is the middle value, and the red circle is your result. The wider pink area represents how common different amounts are, with wider parts showing levels found in more people. Click on each chemical name to compare your exposure to others in the study.


```{r PlotOtherChems, results='asis', echo=FALSE, eval=TRUE}
###
### using variou web links to figure out...this is supposed to work... ineed to check this again...
###  THIS LOOKS GOOD:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops
######   THIS ONE GAVE ANSWER BELOW:  https://stackoverflow.com/questions/61906480/how-to-display-ggplotly-plots-with-dynamically-created-tabs-and-for-loops

plotlyC <- plotlyChems(chemsNOTinConcernGroup, testResults.big, oneResultCalifProp65Risk, oneResultEpaIris, oneResultIARCRisk, chemSourceMitigation)
#cat(" \n about print ploty \n")

if (!is.null(plotlyC)) {
  print(plotlyC)
}
#cat(" \n Just print ploty \n")

```



```{r StatisticsOnAllChemicalsFound, child='StatisticsOnChemicalsFound.Rmd', eval = TRUE}
```


# Chemical Group Information



```{r IndividualClassificationVsAverages, child='YourChemicalsAndAveragesByGroup_text.Rmd', eval = !HideClassificationInformation}
```


```{r IndividualChemicalListWithClassification, child='IndividualChemicalListWithClassification_text.Rmd', eval = !HideClassificationInformation}
```


```{r IndividualChemicalListWithOutClassification, child='IndividualChemicalListWithOutClassification_text.Rmd', eval = HideClassificationInformation}
```



```{r IndividualClassificationShowingChemicals, child='IndividualClassificationShowingChemicals_text.Rmd', eval = !HideClassificationInformation}
```




```{r chart_x5_perc_values, echo=FALSE, message=FALSE, fig.height=12,fig.cap="",dpi=150, eval=FALSE}




## Your Percentage vs Maximum Amount Found

<!--  THIS IS OLD LANGUAGE... improved it somewhat
Another way to view the data is by comparing how much of a chemical you had compared to the maximum found in any wristband. For example, if wristband-A had 100 nanograms and the maximum was 1,000 nanograms, wristband-A had 10% of the maximum. The chart below shows the percentage of the maximum for each chemical found on your wristband.
-->

Next we looking at the amount of each chemical you have compared to the highest amount found on anyone's wristband.  So, if the maximum amount of a certain chemical found was 1,000, and your wristband had 100, you'd have 10% of that maximum. This chart shows you that percentage for all the chemicals found on your wristband, giving you a sense of how your results stack up against the highest levels detected.

`r if(nrow(testResults.big[testResults.big[, "Flag"] == "Y", ])>0){"Any wristbands where we detected a chemical, but could not quantify it, are suppressed from this chart below"}`







################ BEGIN x5 Perc

##
perc_values <- testResults.big %>% #
  filter(SampleNumber == subject) %>%
  filter(Result > 0) %>%
  select(ParameterName, norm_Result)

c <- ggplot(perc_values, aes(y = norm_Result, factor(ParameterName))) +
  # geom_bar(stat="identity")+
  geom_bar(stat = "identity", fill = "blue", colour = "black") +
  labs(
    x = "All Chemicals Found on Your Wristband",
    y = "Percent of Max value Found",
    title = paste(
      "Your Percentage of Max Exposure\n",
      "Found per Chemical\n" # ,
      # "Subject = ", subject
    )
  )
# c

axis.text.x.size <- 6 # JUST changed to be a variable
if (howManyUniqueChemFoundAcrossAllWristbands < 60) axis.text.x.size <- 10
c <- c + theme(
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 90, vjust = .1, hjust = 1, size = axis.text.x.size),
  #           axis.text.x = element_text(angle = 45,vjust=1,hjust=1,size=6 ),

  legend.position = "none",
  panel.background = element_blank(),
  panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  plot.background = element_blank()
)

# c <- c + scale_y_continuous(labels=percent, limits=c(0,1))
c <- c + scale_y_continuous(labels = percent)
c + coord_flip()


rm(c, perc_values)
```

<br>
<br>
