---
output:
  html_document:
    fig_height: 14
    fig_width: 10
    self_contained: true
    mode: selfcontained
    theme: cerulean
    toc: true
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    df_print: "paged"
    keep_md: true
  pdf_document:
    toc: yes
    toc_depth: '3'
  distill::distill_article:
    toc: true
    toc_depth: 4
  word_document:
    reference_docx: MyExposomeFormat_1527_v6.docx
  editor_options: 
  chunk_output_type: console
---

<!-- 
  Themes:
  - cerulean is the BEST so far
  - theme: cerulean
  - theme: sandstone
  - highlight: tango
-->
<!-- 
  NEW IDEA FOR BIG IMPROVEMENT:
  - Read in dataset of ALL DATA COLLECTED PRIOR TO THIS NEW DATASET and then do some analysis
  - New compounds never before seen
  - Compare % of various classifications
  - Etc etc
  BUT THIS IS OUR SECRET SAUCE not to be included/shown to anyone else YET

  SEE THIS location for files that start this:
  D:\Users\Marc\Documents\Kevin Oregon Wristband\DATA\R_analysis\BEST_JULY_2018_DRS_MORE\data\CombinedTestData
-->
<!-- 
  Another idea: new way to do HEAT MAP
  https://themockup.blog/posts/2020-08-28-heatmaps-in-ggplot2/
-->
<!-- 
  LINKS FOR IMPROVING HTML REPORTS:
  - https://holtzy.github.io/Pimp-my-rmd/#github-link (Many ideas for better HTML reports)
  - https://epirhandbook.com/en/heat-plots.html (Great resource)
  - https://bookdown.org/yihui/rmarkdown-cookbook/rgl-3d.html (3D plots)
-->
<!-- 
  NEW IDEA: Techniques to prevent label overlap in GGPLOT2
  https://www.andrewheiss.com/blog/2022/06/23/long-labels-ggplot/
-->
<!-- 
  SEE WORD DOCUMENT:
  Outline of all RMD files and sections.DOCX which has the basic outline
-->
<!-- 
  FUTURE IDEAS TO-DO list:
  - TO MAKE FLOATING HTML TABLE OF CONTENTS
    toc_float: yes
    toc_collapsed: yes
  - #number_sections: yes (Adds section #'s which take up a lot of space)
-->
<!-- 
  GREAT YOUTUBE intro and examples:
  - https://www.youtube.com/watch?v=WkF7nqEYF1E
  - https://github.com/jthomasmock/rmd-nhs
-->
<!-- 
  HTML Tools:
  - https://rstudio.github.io/htmltools/
  - HIDE X axis labels where they will be too scrunched
  - HIDE Y axis labels where they will be too scrunched
  - ADD MESSAGE saying X axis or Y axis is scrunched compressed and contact us for info
-->
<!-- 
  FIGURE OUT SHINY: Seems to be for "live" docs with a server component
  - https://shiny.rstudio.com/tutorial/
-->
<!-- 
  REMEMBER TO USE "addins" "styler" to format code and RMD
-->
<!-- 
  SEE THIS: https://bookdown.org/yihui/rmarkdown/html-document.html
  COOL LINKS:
  - https://garrettgman.github.io/rmarkdown/rmarkdown_websites.html
-->
<!-- 
  Formatting notes:
  - I was using a backslash followed by "s" for newline but changed to just backslash for PDF, HTML, and DOC
  - Changed to <br> for best compatibility
  - Comment size: HTML was height 7, width 6.5 (changing)
  - (comment) RANDOM COMMENT that stays HIDDEN: toc:yes in HTML
  - Update RStudio and all components
  - KEY OBSERVATIONS about 10x values: THIS IS NOW THE BASE VERSION FOR ALL RUNS.
  - USE THIS VERSION FOR EVERY TEST and create new PAH / FLAME / etc from THIS or it won't work.
  - Old config: reference_docx: MyExposomeFormat_20.docx
  - TITLE and AUTHOR set below R code using --- to allow variable use
  - Add MesgV for wristbands with NO compounds found
  - Top section: pdf_document: fig_height: 6.5 keep_tex: yes
-->
 
# TEST TES TES TES TES TEst  asdfasdf fd 
# TEST TES TES TES TES TEst  asdfasdf fd # TEST TES TES TES TES TEst  asdfasdf fd # TEST TES TES TES TES TEst  asdfasdf fd 
 
 
```{r loadAndRunMainCode, echo=FALSE, message=FALSE, include=FALSE}

# THIS FILE requires that an R source file be run first to
#     populate the environment.
#     CAN BE DONE HERE or done before knit'ing this file
   
#test

#
# Set all key variables.  Use the existance (or not) of "subject" to decide if they need to be loaded
if (!exists("subject")) {
  source("MyExp_set_key_variables.R")
}
# This test makes sure that if the SOURCE not yet run, we run it... but don't run it "again"
if (!exists("masterParam")) {
  source(r_code)
}
# This test makes sure that if the SOURCE not yet run, we run it... but don't run it "again"
if (!exists("buildMesgV")) {
  source(support.functions.filename)
}


## THE weird "r include problem Where if I optionally include a RMD file the EVAL value must be an actual value and not a compound value with lots of parts?
##  requires me to calculate this here to use in this RMD instead of using the compound expression
Not_weight_or_time_adjusted <- !(wristbands_weight_adjusted || wristbands_time_adjusted)
NotHideClassificationInformation <- !HideClassificationInformation # WEIRD negation always do to addres RMD call out "eval" function weirdness
is_RMD_type_equal_DRS <- RMD_type == "DRS"
```




```{r loadPNG2, echo=FALSE, message=FALSE , fig.width=3, fig.height=1,fig.cap=""}

# {r loadPNG2, echo=FALSE, message=FALSE , fig.width=3, fig.height=2, fig.align="center"}

img <- readPNG("images/myExposomeLogo.png")
grid.raster(img, name = NULL)
rm(img)
```


```{r loadUCSFPNG2, echo=FALSE, message=FALSE , fig.width=3, fig.height=1,fig.cap="", eval = FALSE}
# note CAN change eval=FAlSE to eval=UCSF2020Fixup

# TEST loading UCSF logo
img <- readPNG("images/UCSF_LOGO_bigger_2.png")
grid.raster(img, name = NULL)
rm(img)
```


---
title: "`r testName`"
author: "MyExposome, Inc."
---

```{r UseSetupGeneralInfoNotSubjectSpecific, echo=FALSE, message=FALSE, include=FALSE}

# !diagnostics suppress=masterParam,testResults.big,class_L,SubClassScores,ParameterID,classification

# Create text string with comma in it for the # of chemicals tested
howManyChemicalsTested <- format(nrow(masterParam), big.mark = ",", scientific = FALSE)

# ONLY USE the non-zero rows in testResult to be sure we're only counting values >0
# Number of total non-zero results divided by # of WBs (that weren't all zero's)
averageNumberChemsFound <- round(nrow(testResults.big[testResults.big$Result > 0, ]) /
  length(unique(testResults.big[testResults.big$Result > 0, ]$SampleNumber)), 1)

# Figure out TOTAL chemicals found ANYWHERE by Classification
CountChemicalsInEachClassification <-
  left_join(
    testResults.big %>% select(ParameterID) %>% distinct(),
    class_L,
    by = "ParameterID"
  ) %>%
  mutate_if(is.factor, as.character) %>%
  group_by(classification) %>%
  dplyr::summarise(TotalFoundAnywhere = dplyr::n())

###### NOW set up class Compare variables
# This WAS in the GROUP COMPARE section but moved up to allow for summary paragrapha at top
# Set up the classCompare variable for later display
# THIS IS MARC new system to find ClassCompare instead of using ClassSub at all
# idea is to use SubClassScores which is a LONG table mapping class/sampleN/Aggregates
#     with another slice of that same table to product an integrated summary
#
#  First build with NO subject column... then add in SUBJECT column later in subject-specific-section
#
ClassCompareNoSubject <- SubClassScores %>%
  group_by(classification) %>%
  summarize(max = max(aggScore), avg = round(mean(aggScore), 1)) %>%
  mutate_if(is.factor, as.character) %>% # Eliminate classification as a FACTOR so it sorts
  arrange(classification)

if (!DoSpecificSubjectAnalysis) { # IF WE do NOT want to do ANY subject SPECIFIC analysis In This Report
  subject <- "Never-Going-to-Match"
}
```


```{r UseSetupSubject, echo=FALSE, message=FALSE, include=FALSE, eval = DoSpecificSubjectAnalysis}

############### REMEMBER TO SET DATA FILE and SUBJECT TO MATCH

# Grab NON-zero rows which match our one subject
oneResult <- testResults.big[testResults.big$Result > 0 & testResults.big$SampleNumber == subject, ]
if (nrow(oneResult) > 0) { # SO if we actually have anything in ONE RESULT THEN we're going to do something... otherwise just nonsense
  oneResult_with_Y_flag <- testResults.big[(testResults.big$Flag == "Y" | testResults.big$Result > 0) & testResults.big$SampleNumber == subject, ]
  # Sort Test Results by ParameterName
  oneResult <- arrange(oneResult, ParameterName)
  # Find PureSampleName of this sample
  pureSubjectName <- oneResult[1, "PureSampleName"]
} else {
  oneResult_with_Y_flag <- oneResult
  pureSubjectName <- oneResult
}


# howManyChemsFoundThisWristband <- nrow(testResults[testResults$SampleNumber==subject,])
# ONLY USE the non-zero rows in testResult to be sure we're only counting values >0
howManyChemicalsFoundThisWristband <- nrow(oneResult_with_Y_flag)


### TO DO
### TO DO   NEED to continue to fix Y flag stuf for Individual User
### TO DO
### TO DO

## Now try and find the median/min/max/sddev for each chemical found


# statSummary


###### NOW set up class Compare variables
# This WAS in the GROUP COMPARE section but moved up to allow for summary paragrapha at top
# Set up the classCompare variable for later display
### idea is to smash together summarized data with just one column of data by using JOIN
####    LEFT join is key cause "any found category" is superset of "categories of this subject"
### so the two things we "join" are a summarization of the LONG classification of all subjects SCORES
#       with the scores for this individual subject
# ONCE we've joined those together then PIPE it over to select our columns/elim NA/arrange

ClassCompareSubject <- left_join(
  ClassCompareNoSubject %>% mutate_if(is.factor, as.character),
  SubClassScores[SubClassScores$SampleNumber == subject, ] %>% mutate_if(is.factor, as.character),
  by = "classification"
) %>%
  arrange(classification) %>%
  dplyr::rename(Participant = aggScore, Average = avg, maxFoundAnyOneBand = max) %>%
  select(classification, Participant, Average, maxFoundAnyOneBand) %>%
  replace_na(list(Participant = 0))
```



```{r separateNoteToSelf, echo=FALSE, message=FALSE, include=FALSE}

## NOTES ON FUTURE "DO TO" with this RMD file
####  DONE SOMEWHAT  Add copyright and LIMITS OF LIABILITY to end of report.
#
# and SEE OTHER COMMENTS up at top of this doc
```

# Introduction and Summary


<!-- PRINT MESSAGE ABOUT WHAT COMPANY THIS TEST WAS DONE "FOR" -->
`r if(testDoneFor != ""){ paste("**This test was done for:     ",testDoneFor, "**")   }`


<!-- RUN RMD TO PRINT MESSAGE INTRO'ING THE GROUP REPORT (WITH NO INDIVIDUAL REPORT) -->
```{r GroupAnalysisIntro, child='GroupAnalysisIntro_text.Rmd', eval = DoGroupAnalysisOnly}

```

<!-- RUN RMD TO PRINT MESSAGE INTRO'ING THE INDIVUDAL AND GROUP REPORT -->
```{r SpecificSubjectAnalysisIntro, child='SpecificSubjectAnalysisIntro_text.Rmd', eval=DoSpecificSubjectAnalysis}

```





```{r  IRiS_Prop65_IARC_Group_Results, results='asis', echo=FALSE, message=FALSE}

# Calculate epa IRIS results but display it later

# FOR ALL CHEMICALS FOUND on ANY wristband
# Figure how WHAT the hits were on each database of bad chems
# and figure out how-many hits

# FOR EPAIRIS
# Find all hits agaisnt this DB found in any wristband
EPAirisHits <- testResults.big %>%
  mutate(Result = case_when(
    Flag == "Y" ~ 100,
    TRUE ~ Result
  )) %>% # IF we have a Y flag on an item set the ZERO value to 100
  filter(Result > 0) %>%
  select(ParameterID, ParameterName) %>%
  distinct() %>%
  inner_join(epaIris, by = "ParameterID") %>%
  select(ParameterName, IRIS_Summary) %>%
  dplyr::rename("Chemical Name" = ParameterName, "IRIS Summary Web Link" = IRIS_Summary)

# FOR EPA IRIS count'm up
countEPAiristHits <- nrow(EPAirisHits)

#--------------------------

# calculate PROP 65 results, print later

# Find all hits agaisnt this DB found in any wristband
CalifProp65Hits <- testResults.big %>%
  mutate(Result = case_when(
    Flag == "Y" ~ 100,
    TRUE ~ Result
  )) %>% # IF we have a Y flag on an item set the ZERO value to 100
  filter(Result > 0) %>%
  select(ParameterID, ParameterName) %>%
  distinct() %>%
  inner_join(riskCalifProp65, by = "ParameterID") %>%
  select(ParameterName, toxicityType) %>%
  dplyr::rename("Chemical Name" = ParameterName, "Risk Type Per California Prop 65" = toxicityType)


# FOR Prop 65 count'm up
countCalifProp65Hits <- nrow(CalifProp65Hits)


# calculate IARC results, print later

# Find all hits agaisnt this DB found in any wristband
IARCHits <- testResults.big %>%
  mutate(Result = case_when(
    Flag == "Y" ~ 100,
    TRUE ~ Result
  )) %>% # IF we have a Y flag on an item set the ZERO value to 100
  filter(Result > 0) %>%
  select(ParameterID, ParameterName) %>%
  distinct() %>%
  inner_join(IARCRisk, by = "ParameterID") %>%
  select(ParameterName, IARC_Classification) %>%
  dplyr::rename("Chemical Name" = ParameterName, "Risk Type Per IARC" = IARC_Classification)


# FOR Prop 65 count'm up
countIARCHits <- nrow(IARCHits)
```



```{r IRiS_Prop65_IARC_Individual_Results, results='asis', echo=FALSE, message=FALSE, eval=DoSpecificSubjectAnalysis}


# Calculate epa IRIS results but display it later

#  Join our results on one subject with classification table to get classification(s) of each chem
#  DO THIS without using SQL
#  Do this for ONERESULT
oneResultEpaIris <- inner_join(oneResult_with_Y_flag, epaIris, by = "ParameterID") %>%
  select(ParameterName, IRIS_Summary) %>%
  arrange(ParameterName)

names(oneResultEpaIris) <- c("Chemical Name", "IRIS Summary Web Link")

numEPAirisFound <- nrow(oneResultEpaIris)



# calculate califProp65 results but print later

#  Join our results on one subject with classification table to get classification(s) of each chem
# Without using SQL
oneResultCalifProp65Risk <- inner_join(oneResult_with_Y_flag, riskCalifProp65, by = "ParameterID") %>%
  select(ParameterName, Risk_Description = toxicityType) %>%
  arrange(ParameterName)

names(oneResultCalifProp65Risk) <- c("Chemical Name", "Risk Type Per California Prop 65")

# #How many were found?
numCalProp65Found <- nrow(oneResultCalifProp65Risk)
#



# rm(riskCalifProp65)

# calculate IARC results, print later

#  Join our results on one subject with classification table to get classification(s) of each chem
# Without using SQL
oneResultIARCRisk <- inner_join(oneResult_with_Y_flag, IARCRisk, by = "ParameterID") %>%
  select(ParameterName, IARC_Classification) %>%
  arrange(ParameterName)

# Rename the two columns
names(oneResultIARCRisk) <- c("Chemical Name", "Risk Type Per IARC")

# How many were found
numIARCRiskFound <- nrow(oneResultIARCRisk)
```



<!-- PRINT Headline Rule on NumChems as denoted by Silent Spring -->
```{r HeadlineMessageTotalNumChems, child='HeadlineMessageTotalChems.Rmd', eval = TRUE}

```



<!-- PRINT Headline Rule on NumChems as denoted by Silent Spring -->
```{r HeadlinesAmountByChemicalGroup, child='HeadlinesAmountByChemicalGroup.Rmd', eval = FALSE}

```





## List of Key Observations
```{r BuildMessageString, results='asis', echo=FALSE, message=FALSE}

# COMMENTS BY MARC:  We are building a MESSAGE STRING = "mesg.v"
# and we will keep concatenating onto "mesg.v" with whatever new information we can
#

# Initialize mesg  to NULL
mesg.v <- NULL # and use a vector

### INDIVIDUAL RESULTS COME FIRST:
####### add line to indicate start of INDIVIDUAL results

if (DoSpecificSubjectAnalysis) {
  mesg.v <- addMesg(mesg.v, 1, " ", "**INDIVIDUAL RESULTS**")
  # Add things to mesg vector using a function call to support functions
  mesg.v <- buildMesgVIndividual(
    testResults.big,
    mesg.v,
    subject,
    SubClassScores,
    results_W,
    numEPAirisFound,
    numCalProp65Found,
    numIARCRiskFound
  )
}

### GROUP RESULTS COME AFTER INDIVIDUAL RESULTS
####### add line to indicate start of GROUP results
mesg.v <- addMesg(mesg.v, 1, " ", "**GROUP RESULTS**")
# Add things to mesg vector using a function call to support functions
mesg.v <- buildMesgVGroup(
  testResults.big,
  mesg.v,
  SubClassScores,
  results_W,
  countEPAiristHits,
  countCalifProp65Hits,
  countIARCHits
)


pandoc.list(mesg.v) ## This prints the Individual Band (if doing) and Group bands report(s)
rm(mesg.v)


if (DoSpecificSubjectAnalysis) {
  rm(numIARCRiskFound, numCalProp65Found, numEPAirisFound)
}

# rm(buildMesgV) # can't really remove this cause I'm using this as a flag to see if need to reload
```


`r if(nrow(testResults.big[testResults.big[, "Flag"] == "Y", ]) >0){
                            paste("**IMPORTANT NOTE:     ",length(unique(testResults.big[testResults.big[, "Flag"] == "Y", ]$ParameterName)),
                            "of the tested compounds impacting ",
                            length(unique(testResults.big[testResults.big[, "Flag"] == "Y", ]$SampleNumber)),
                            "wristbands could not be fully quantified.**")
                            }`
`r if(nrow(testResults.big[testResults.big[, "Flag"] == "Y", ]) >0){
                            paste("\n Due instrument challenges some chemicals were present but could not be quantified.",
                              "For reporting below, where numbers are needed, these specific results are counted as though",
                              "they detected zero because we don't have an actual number to use in this report",
                              "but we can report that these compounds were definitely detected on these wristbands")
                            }`
                            



```{r BuildCaveatMessageString, results='asis', echo=FALSE, message=FALSE}

### IMPORTANT CAVEATS That MUST be added
### NOTE:  at the moment, the only caveat is the "Y" caveat

### HERE IS SOME R error with below code, generating a WARNING for now... no idea why
#
# Warning message:
# The `i` argument of ``[`()` can't be a matrix as of tibble 3.0.0.
# Convert to a vector.
# This warning is displayed once every 8 hours.
# ## FIXED FIXED FIXED

if (any(testResults.big[, "Flag"] == "Y")) { # testing if we have any "Y"
  mesg.v2 <- NULL
  testResultsWith_Y_Flag <- arrange(testResults.big[testResults.big[, "Flag"] == "Y", ], ParameterName)
  for (i in 1:nrow(testResultsWith_Y_Flag)) {
    row <- testResultsWith_Y_Flag[i, ]
    txt <- paste(row$ParameterName, "was detected on wristband:", row$SampleNumber)
    mesg.v2 <- cbind(mesg.v2, txt)
  }
  pandoc.list(mesg.v2) ## This prints the Individual Band (if doing) and Group bands report(s)
  rm(mesg.v2, testResultsWith_Y_Flag)
}

# rm(buildMesgV) # can't really remove this cause I'm using this as a flag to see if need to reload
```

<br>

<!-- PRINT DESCRIPTION OF EACH CLASSIFICATION -->
```{r CompoundClassification, child='CompoundClassification_text.Rmd', eval = NotHideClassificationInformation}

```


<!-- SHOW RESULTS FOR INDIVIDUAL SUBJECT IF DESIRED DELETING THIS DELETE THIS DELETE THIS EVENTUALLY when we have violin charts working-->
```{r IndividualResultsAnalysis_DELETING_EVENTUALLY, child='IndividualResultsAnalysis_text.Rmd', eval = FALSE}
```

<!-- SHOW RESULTS FOR INDIVIDUAL SUBJECT IF DESIRED -->
```{r IndividualResultsAnalysis, child='IndividualResultsAnalysis__w_Violin_text.Rmd', eval = DoSpecificSubjectAnalysis}

```



<!-- SHOW RESULTS FOR FULL GROUP -->
```{r GroupResultsAnalysis, child='GroupResultsAnalysis.Rmd', eval = TRUE}

```


```{r testingPrePostProcessing, child='testPrePostProcessing.Rmd', eval = (testing_PRE_POST && nrow(testResultsPrePost)>=2) }

```


```{r  AdditionalInformation, child='AdditionalInformation.Rmd' }

```
