---
params:
  logo_path: "images/myExposomeLogo_with_transparent_padding25.png"
output:
  rmdformats::readthedown:       #rmdformats::readthedown:
    self_contained: true
    number_sections: true
    css: "customMyExp.css" # Use CSS to change color scheme from Red/Black to BLUE/black for readthedown rmdformat
              # base_url: ""   ###  This is not needed, did it because if right click download was converting links from relative to absolute
              # and the CSS does lots of stuff to control how it prints
    toc_depth: 3   # DELETE/COMMENT this line for some rmdformats      toc_depth: 3
    df_print: "paged"
    lightbox: true   # Enables the lightbox for clickable images
    gallery: true    # Groups images into a gallery with navigation between images
    thumbnails: false # Images will appear at their original size
  distill::distill_article:
    toc: true
    toc_depth: 4
  word_document:
    reference_docx: MyExposomeFormat_1527_v6.docx
  pdf_document:
    toc: yes
    toc_depth: '3'
  editor_options: 
    chunk_output_type: console
---

<!--
•	1  Project Root                                                    
•	2   °--MyExposome_1527_v6.Rmd                                      
•	3       ¦--SpecificSubjectAnalysisIntro_text.Rmd                   
•	4       ¦--GroupAnalysisIntro_text.Rmd                             
•	5       ¦--GroupAndIndividualAnalysisIntro_text.Rmd                
•	6       ¦--HeadlineMessageTotalChems.Rmd                           
•	7       ¦--HeadlinesAmountByChemicalGroup.Rmd                      
•	8       ¦--IndividualResultsAnalysis__w_Violin_text.Rmd            
•	9       ¦   ¦--StatisticsOnChemicalsFound.Rmd                      
•	10      ¦   ¦--YourChemicalsAndAveragesByGroup_text.Rmd            
•	11      ¦   ¦--IndividualChemicalListWithClassification_text.Rmd   
•	12      ¦   ¦--IndividualChemicalListWithOutClassification_text.Rmd
•	13      ¦   °--IndividualClassificationShowingChemicals_text.Rmd   
•	14      ¦--CompoundClassification_text.Rmd                         
•	15      ¦--GroupResultsAnalysis.Rmd                                
•	16      ¦   ¦--GroupDatabaseLookupIARC_Prop65_IRIS.Rmd             
•	17      ¦   ¦--GroupChemicalListWithClassification_text.Rmd        
•	18      ¦   ¦--GroupChemicalListWithOutClassification_text.Rmd     
•	19      ¦   ¦--airConcentrationOutput.Rmd                          
•	20      ¦   ¦--GroupClassificationAnyWristband_text.Rmd            
•	21      ¦   ¦--StatisticsOnChemicalsFound.Rmd                      
•	22      ¦   ¦--GroupClassificationAtLeastOne_text.Rmd              
•	23      ¦   ¦--GroupClassificationEveryWristband_text.Rmd          
•	24      ¦   °--loreal_venn_text.Rmd                                
•	25      ¦--testPrePostProcessing.Rmd                               
•	26      °--AdditionalInformation.Rmd   

-->

```{r loadAndRunMainCode, echo=FALSE, message=FALSE, include=FALSE}
# THIS FILE requires that an R source file be run first to
#     populate the environment.
#     CAN BE DONE HERE or done before knit'ing this file

# test
#cat("222 Starting the RMarkdown execution...\n", file = "debug_log.txt", append = TRUE)

library(here)
setwd(here::here())  
##source(here::here("R", ""))
#cat("333 Starting the RMarkdown execution...\n", file = "debug_log.txt", append = TRUE)


#
# Set all key variables.  Use the existance (or not) of "subject" to decide if they need to be loaded
if (!exists("subject")) {
  #source("MyExp_set_key_variables.R")
  if (exists("setRdirectory")){
    source(setRdirectory("MyExp_set_key_variables.R"))
  } else {  # IF we don't have a function yet to set R directory, set it manually here
    source(here::here("R","MyExp_set_key_variables.R"))
  }
}
#cat("444 Starting the RMarkdown execution...\n", file = "debug_log.txt", append = TRUE)


# This test makes sure that if the SOURCE not yet run, we run it... but don't run it "again"
## ALSO:  FROM HERE ON all paths should be handled already by functions, just use file names unless something hard-coded inline
if (!exists("masterParam")) {
  source(r_code)
}

#cat("555 Starting the RMarkdown execution...\n", file = "debug_log.txt", append = TRUE)

# This test makes sure that if the SOURCE not yet run, we run it... but don't run it "again"
if (!exists("buildMesgV")) {
  source(support.functions.filename)
}
#cat("222 Starting the RMarkdown execution...\n", file = "debug_log.txt", append = TRUE)

## THE weird "r include problem Where if I optionally include a RMD file the EVAL value must be an actual value and not a compound value with lots of parts?
##  requires me to calculate this here to use in this RMD instead of using the compound expression
##   THIS GOT FIXED SOMEWHERE so ... i 'm commenting all these out for now!
# Not_weight_or_time_adjusted <- !(wristbands_weight_adjusted || wristbands_time_adjusted)
# NotHideClassificationInformation <- !HideClassificationInformation # WEIRD negation always do to addres RMD call out "eval" function weirdness
# is_RMD_type_equal_DRS <- RMD_type == "DRS"

## This logo stuff is to include the MyExposome logo in the report.  I had trouble so converted logo to base64 
###            cause path kept getting messed up for print-all-subjects
###  NORMALLY i wanted to put all paths in to initiation area and not say "images"here but leaving this alone cause tempermental code
logo_path <- here::here("images", "myExposomeLogo_with_transparent_padding25.png")
image_base64 <- dataURI(file = logo_path, mime = "image/png")
```

```{r loadPNG2, echo=FALSE, message=FALSE , fig.width=3, fig.height=1,fig.cap="" , eval=FALSE}
# stop putting image at top of big content cause i'm styling onto the sisdebar

# {r loadPNG2, echo=FALSE, message=FALSE , fig.width=3, fig.height=2, fig.align="center"}

# img <- readPNG("images/myExposomeLogo.png")
img <- readPNG("images/myExposomeLogo50smaller.png")
grid.raster(img, name = NULL)
rm(img)
```

```{r loadUCSFPNG2, echo=FALSE, message=FALSE , fig.width=3, fig.height=1,fig.cap="", eval= FALSE}
# note CAN change eval=FAlSE to eval=UCSF2020Fixup

# TEST loading UCSF logo
img <- readPNG("images/UCSF_LOGO_bigger_2.png")
grid.raster(img, name = NULL)
rm(img)
```



<!-- DIV in html to insert the logo but only do this when PRINTING --> 

<div id="print-logo">
  <img src="`r image_base64`" alt="Company Logo" style="width: 800px;">
</div>


---
title: "`r testName`"
author: "MyExposome, Inc."
---

<script>
  var logoPath = "`r image_base64`";  // Set to Base64 Data URI
</script>

<!-- JavaScript to insert the logo after the TOC --> 
<script> 
document.addEventListener("DOMContentLoaded", function() 
{ var toc = document.querySelector("#sidebar #toc"); 
if (toc) { var logo = document.createElement("img"); 
      logo.src = logoPath;  // Use the Base64 Data URI
// Adjust path if needed 
logo.alt = "Logo"; logo.style.width = "100%"; 
// Adjust size as needed 
logo.style.margin = "15px 0"; 
// Add spacing 
toc.insertAdjacentElement("afterend", logo); } }); 
</script> 



```{r UseSetupGeneralInfoNotSubjectSpecific, echo=FALSE, message=FALSE, include=FALSE}
# !diagnostics suppress=masterParam,testResults.big,class_L,SubClassScores,ParameterID,classification

# Create text string with comma in it for the # of chemicals tested
howManyChemicalsTested <- format(nrow(masterParam), big.mark = ",", scientific = FALSE)

# ONLY USE the non-zero rows in testResult to be sure we're only counting values >0
# Number of total non-zero results divided by # of WBs (that weren't all zero's)
averageNumberChemsFound <- round(nrow(testResults.big[testResults.big$Result > 0, ]) /
  length(unique(testResults.big[testResults.big$Result > 0, ]$SampleNumber)), 1)

# Figure out TOTAL chemicals found ANYWHERE by Classification
CountChemicalsInEachClassification <-
  left_join(
    testResults.big %>% select(ParameterID) %>% distinct(),
    class_L,
    by = "ParameterID"
  ) %>%
  mutate_if(is.factor, as.character) %>%
  group_by(classification) %>%
  dplyr::summarise(TotalFoundAnywhere = dplyr::n())

###### NOW set up class Compare variables
# This WAS in the GROUP COMPARE section but moved up to allow for summary paragrapha at top
# Set up the classCompare variable for later display
# THIS IS MARC new system to find ClassCompare instead of using ClassSub at all
# idea is to use SubClassScores which is a LONG table mapping class/sampleN/Aggregates
#     with another slice of that same table to product an integrated summary
#
#  First build with NO subject column... then add in SUBJECT column later in subject-specific-section
#
ClassCompareNoSubject <- SubClassScores %>%
  group_by(classification) %>%
  summarize(max = max(aggScore), avg = round(mean(aggScore), 1)) %>%
  mutate_if(is.factor, as.character) %>% # Eliminate classification as a FACTOR so it sorts
  arrange(classification)

if (!DoSpecificSubjectAnalysis) { # IF WE do NOT want to do ANY subject SPECIFIC analysis In This Report
  subject <- "Never-Going-to-Match"
}
```

```{r UseSetupSubject, echo=FALSE, message=FALSE, include=FALSE, eval= DoSpecificSubjectAnalysis}
############### REMEMBER TO SET DATA FILE and SUBJECT TO MATCH

# Grab NON-zero rows which match our one subject
oneResult <- testResults.big[testResults.big$Result > 0 & testResults.big$SampleNumber == subject, ]
if (nrow(oneResult) > 0) { # SO if we actually have anything in ONE RESULT THEN we're going to do something... otherwise just nonsense
  oneResult_with_Y_flag <- testResults.big[(testResults.big$Flag == "Y" | testResults.big$Result > 0) & testResults.big$SampleNumber == subject, ]
  # Sort Test Results by ParameterName
  oneResult <- arrange(oneResult, ParameterName)
  # Find PureSampleName of this sample
  pureSubjectName <- oneResult[1, "PureSampleName"]$PureSampleName
} else {
  oneResult_with_Y_flag <- oneResult
  pureSubjectName <- "NO VALUES FOUND FOR THIS WRISTBAND"
}



# howManyChemsFoundThisWristband <- nrow(testResults[testResults$SampleNumber==subject,])
# ONLY USE the non-zero rows in testResult to be sure we're only counting values >0
howManyChemicalsFoundThisWristband <- nrow(oneResult_with_Y_flag)


### TO DO
### TO DO   NEED to continue to fix Y flag stuf for Individual User
### TO DO
### TO DO

## Now try and find the median/min/max/sddev for each chemical found


# statSummary


###### NOW set up class Compare variables
# This WAS in the GROUP COMPARE section but moved up to allow for summary paragrapha at top
# Set up the classCompare variable for later display
### idea is to smash together summarized data with just one column of data by using JOIN
####    LEFT join is key cause "any found category" is superset of "categories of this subject"
### so the two things we "join" are a summarization of the LONG classification of all subjects SCORES
#       with the scores for this individual subject
# ONCE we've joined those together then PIPE it over to select our columns/elim NA/arrange

ClassCompareSubject <- left_join(
  ClassCompareNoSubject %>% mutate_if(is.factor, as.character),
  SubClassScores[SubClassScores$SampleNumber == subject, ] %>% mutate_if(is.factor, as.character),
  by = "classification"
) %>%
  arrange(classification) %>%
  dplyr::rename(Participant = aggScore, Average = avg, maxFoundAnyOneBand = max) %>%
  select(classification, Participant, Average, maxFoundAnyOneBand) %>%
  replace_na(list(Participant = 0))
```

 
# Introduction and Summary

<!-- PRINT MESSAGE ABOUT WHAT COMPANY THIS TEST WAS DONE "FOR" -->

`r if(testDoneFor != ""){ paste("**This test was done for    ",testDoneFor, "**.")   }`

<!-- RUN RMD TO PRINT MESSAGE INTRO'ING THE INDIVUDAL REPORT -->

```{r SpecificSubjectAnalysisIntro, child='SpecificSubjectAnalysisIntro_text.Rmd', eval=(DoSpecificSubjectAnalysis && !DoGroupAnalysis) }
```

<!-- RUN RMD TO PRINT MESSAGE INTRO'ING THE GROUP REPORT (WITH NO INDIVIDUAL REPORT) -->

```{r GroupAnalysisIntro, child='GroupAnalysisIntro_text.Rmd', eval= (DoGroupAnalysis && !DoSpecificSubjectAnalysis) }
```

<!-- RUN RMD TO PRINT MESSAGE INTRO'ING THE  INDIVIDUAL REPORT and GROUP MESSAGE -->

```{r GroupAndIndividualAnalysisIntro, child='GroupAndIndividualAnalysisIntro_text.Rmd', eval= (DoSpecificSubjectAnalysis && DoGroupAnalysis)}
```

```{r  IRiS_Prop65_IARC_Group_Results, results='asis', echo=FALSE, message=FALSE}
# Calculate epa IRIS results but display it later

# FOR ALL CHEMICALS FOUND on ANY wristband
# Figure how WHAT the hits were on each database of bad chems
# and figure out how-many hits

# FOR EPAIRIS
# Find all hits agaisnt this DB found in any wristband
EPAirisHits <- testResults.big %>%
  mutate(Result = case_when(
    Flag == "Y" ~ 100,
    TRUE ~ Result
  )) %>% # IF we have a Y flag on an item set the ZERO value to 100
  filter(Result > 0) %>%
  select(ParameterID, ParameterName) %>%
  distinct() %>%
  inner_join(epaIris, by = "ParameterID") %>%
  select(ParameterName, IRIS_Summary) %>%
  dplyr::rename("Chemical Name" = ParameterName, "IRIS Summary Web Link" = IRIS_Summary)

# FOR EPA IRIS count'm up
countEPAiristHits <- nrow(EPAirisHits)

#--------------------------

# calculate PROP 65 results, print later

# Find all hits agaisnt this DB found in any wristband
CalifProp65Hits <- testResults.big %>%
  mutate(Result = case_when(
    Flag == "Y" ~ 100,
    TRUE ~ Result
  )) %>% # IF we have a Y flag on an item set the ZERO value to 100
  filter(Result > 0) %>%
  select(ParameterID, ParameterName) %>%
  distinct() %>%
  inner_join(riskCalifProp65, by = "ParameterID") %>%
  select(ParameterName, toxicityType) %>%
  dplyr::rename("Chemical Name" = ParameterName, "Risk Type Per California Prop 65" = toxicityType)


# FOR Prop 65 count'm up
countCalifProp65Hits <- nrow(CalifProp65Hits)


# calculate IARC results, print later

# Find all hits agaisnt this DB found in any wristband
IARCHits <- testResults.big %>%
  mutate(Result = case_when(
    Flag == "Y" ~ 100,
    TRUE ~ Result
  )) %>% # IF we have a Y flag on an item set the ZERO value to 100
  filter(Result > 0) %>%
  select(ParameterID, ParameterName) %>%
  distinct() %>%
  inner_join(IARCRisk, by = "ParameterID") %>%
  select(ParameterName, IARC_Classification) %>%
  dplyr::rename("Chemical Name" = ParameterName, "Risk Type Per IARC" = IARC_Classification)


# FOR Prop 65 count'm up
countIARCHits <- nrow(IARCHits)
```

```{r IRiS_Prop65_IARC_Individual_Results, results='asis', echo=FALSE, message=FALSE, eval=DoSpecificSubjectAnalysis}
# Calculate epa IRIS results but display it later

#  Join our results on one subject with classification table to get classification(s) of each chem
#  DO THIS without using SQL
#  Do this for ONERESULT
oneResultEpaIris <- inner_join(oneResult_with_Y_flag, epaIris, by = "ParameterID") %>%
  select(ParameterName, IRIS_Summary) %>%
  arrange(ParameterName)

names(oneResultEpaIris) <- c("Chemical Name", "IRIS Summary Web Link")

numEPAirisFound <- nrow(oneResultEpaIris)



# calculate califProp65 results but print later

#  Join our results on one subject with classification table to get classification(s) of each chem
# Without using SQL
oneResultCalifProp65Risk <- inner_join(oneResult_with_Y_flag, riskCalifProp65, by = "ParameterID") %>%
  select(ParameterName, Risk_Description = toxicityType) %>%
  arrange(ParameterName)

names(oneResultCalifProp65Risk) <- c("Chemical Name", "Risk Type Per California Prop 65")

# #How many were found?
numCalProp65Found <- nrow(oneResultCalifProp65Risk)
#



# rm(riskCalifProp65)

# calculate IARC results, print later

#  Join our results on one subject with classification table to get classification(s) of each chem
# Without using SQL
oneResultIARCRisk <- inner_join(oneResult_with_Y_flag, IARCRisk, by = "ParameterID") %>%
  select(ParameterName, IARC_Classification) %>%
  arrange(ParameterName)

# Rename the two columns  
names(oneResultIARCRisk) <- c("Chemical Name", "Risk Type Per IARC")

# How many were found
numIARCRiskFound <- nrow(oneResultIARCRisk)
```

<!-- PRINT Headline Rule on NumChems as denoted by Silent Spring  THIS ONLY WORKS IF THERE IS INDIVIDUAL REPORT GOING ON... NOT FOR GROUP ONLY...-->
<!-- r HeadlineMessageTotalNumChems, child='HeadlineMessageTotalChems.Rmd', eval= DoSpecificSubjectAnalysis -->

```{r HeadlineMessageTotalNumChems, child='HeadlineMessageTotalChems.Rmd', eval= DoSpecificSubjectAnalysis}
```

<!-- PRINT Headline Rule on NumChems as denoted by Silent Spring -->
<!-- r HeadlinesAmountByChemicalGroup, child='HeadlinesAmountByChemicalGroup.Rmd', eval= DoSpecificSubjectAnalysis -->

```{r HeadlinesAmountByChemicalGroup, child='HeadlinesAmountByChemicalGroup.Rmd', eval= DoSpecificSubjectAnalysis}
```

## Observations

```{r BuildMessageString, results='asis', echo=FALSE, message=FALSE}
# COMMENTS BY MARC:  We are building a MESSAGE STRING = "mesg.v"
# and we will keep concatenating onto "mesg.v" with whatever new information we can
#

# Initialize mesg  to NULL
mesg.v <- NULL # and use a vector

### INDIVIDUAL RESULTS COME FIRST:
####### add line to indicate start of INDIVIDUAL results

if (DoSpecificSubjectAnalysis) {
  if (DoGroupAnalysis) {
    mesg.v <- addMesg(mesg.v, 1, " ", "**INDIVIDUAL RESULTS**")
  }
  # Add things to mesg vector using a function call to support functions
  mesg.v <- buildMesgVIndividual(
    testResults.big,
    mesg.v,
    subject,
    SubClassScores,
    results_W,
    numEPAirisFound,
    numCalProp65Found,
    numIARCRiskFound,
    howManyWristbandsTested,
    HideClassificationInformation
  )
}

### GROUP RESULTS COME AFTER INDIVIDUAL RESULTS
####### add line to indicate start of GROUP results

if (DoGroupAnalysis) {
  mesg.v <- addMesg(mesg.v, 1, " ", "**GROUP RESULTS**")
  # Add things to mesg vector using a function call to support functions
  mesg.v <- buildMesgVGroup(
    testResults.big,
    mesg.v,
    SubClassScores,
    results_W,
    countEPAiristHits,
    countCalifProp65Hits,
    countIARCHits,
    HideClassificationInformation
  )
}


pandoc.list(mesg.v) ## This prints the Individual Band (if doing) and Group bands report(s)
rm(mesg.v)


if (DoSpecificSubjectAnalysis) {
  rm(numIARCRiskFound, numCalProp65Found, numEPAirisFound)
}

# rm(buildMesgV) # can't really remove this cause I'm using this as a flag to see if need to reload
```

`r if (nrow(testResults.big[testResults.big[, "Flag"] == "Y", ]) > 0)
  
{
  paste(
    "**NOTE:     ",
    length(unique(testResults.big[testResults.big[, "Flag"] == "Y", ]$ParameterName)),
    "of the tested compounds impacting ",
    length(unique(testResults.big[testResults.big[, "Flag"] == "Y", ]$SampleNumber)),
    "wristbands could not be fully quantified.**"
  )
}` `r if (nrow(testResults.big[testResults.big[, "Flag"] == "Y", ]) > 0)
{
  paste(
    "\n Due instrument challenges some chemicals were present but could not be quantified.",
    "For reporting below, where numbers are needed, these specific results are counted as though",
    "they detected zero because we don't have an actual number to use in this report",
    "but we can report that these compounds were definitely detected on these wristbands"
  )
}`

```{r BuildCaveatMessageString, results='asis', echo=FALSE, message=FALSE}
### IMPORTANT CAVEATS That MUST be added
### NOTE:  at the moment, the only caveat is the "Y" caveat

### HERE IS SOME R error with below code, generating a WARNING for now... no idea why
#
# Warning message:
# The `i` argument of ``[`()` can't be a matrix as of tibble 3.0.0.
# Convert to a vector.
# This warning is displayed once every 8 hours.
# ## FIXED FIXED FIXED

if (any(testResults.big[, "Flag"] == "Y")) { # testing if we have any "Y"
  mesg.v2 <- NULL
  testResultsWith_Y_Flag <- arrange(testResults.big[testResults.big[, "Flag"] == "Y", ], ParameterName)
  for (i in 1:nrow(testResultsWith_Y_Flag)) {
    row <- testResultsWith_Y_Flag[i, ]
    txt <- paste(row$ParameterName, "was detected on wristband:", row$SampleNumber)
    mesg.v2 <- cbind(mesg.v2, txt)
  }
  pandoc.list(mesg.v2) ## This prints the Individual Band (if doing) and Group bands report(s)
  rm(mesg.v2, testResultsWith_Y_Flag)
}

# rm(buildMesgV) # can't really remove this cause I'm using this as a flag to see if need to reload
```

<br>

<!-- SHOW RESULTS FOR INDIVIDUAL SUBJECT IF DESIRED -->

```{r IndividualResultsAnalysis, child='IndividualResultsAnalysis__w_Violin_text.Rmd', eval= DoSpecificSubjectAnalysis}
```

<!-- PRINT DESCRIPTION OF EACH CLASSIFICATION -->

```{r CompoundClassification, child='CompoundClassification_text.Rmd', eval= !HideClassificationInformation}
```

<!-- SHOW RESULTS FOR FULL GROUP -->

```{r GroupResultsAnalysis, child='GroupResultsAnalysis.Rmd', eval= DoGroupAnalysis}
```

```{r testingPrePostProcessing, child='testPrePostProcessing.Rmd', eval= (testing_PRE_POST && nrow(testResultsPrePost)>=2) }
```

```{r  AdditionalInformation, child='AdditionalInformation.Rmd' }
```

<!-- Add a button to print the report -->
<div style="text-align: right; margin-top: 20px;">
  <button onclick="window.print()" class="btn btn-success" style="color: white; background-color: #1a3edd; border-radius: 8px; padding: 10px 20px; font-size: 16px; cursor: pointer;">
    <i class="fa fa-print"></i> Print Report
  </button>
</div>

