


```{r setupbs_modal_std_dev, echo=FALSE}


bs_modal(id = "StandardDevation", title = "Standard Deviation Definition", body = "Standard deviation is a measure of how spread out the numbers in a set are from the average. A bigger standard deviation means the numbers are more spread out, while a smaller one means they're closer to the average.")

stdDevButton<-bs_button("standard deviation", button_type = "primary", class = "btn-xs btn-outline-info") %>% bs_attach_modal(id_modal = "StandardDevation")


# REMEMBER here is how to use a button
# bs_button("Standard Devation", button_type = "primary", class = "btn-xs btn-outline-info") %>%
#  bs_attach_modal(id_modal = "StandardDevation")

#One important way to look at the data is, for each chemical, what was the smallest, largest, average, and middle value found, how many wristbands was it found on, and the `r bs_button("standard deviation", button_type = "primary", class = "btn-xs btn-outline-info") %>% bs_attach_modal(id_modal = "StandardDevation")`.

  
```


## Statistics on Chemicals Found


One important way to look at the data is, for each chemical, what was the smallest, largest, average, and middle value found, how many wristbands was it found on, and the `r stdDevButton`. The wristbands were tested for different chemicals. The results show how much of each chemical was found, adjusted for the time worn.  Anything we couldn't clearly detect was left out of the table below.


```{r print_not_time_or_weight_adjust, results="asis", echo=FALSE, eval=!(wristbands_weight_adjusted || wristbands_time_adjusted)}
cat("The data is the raw nanograms found in each wristband. ", sep = "")
```

```{r print_weight_only_adjust1, results="asis", echo=FALSE, eval=wristbands_weight_adjusted}
cat("The data is the raw nanograms found in each gram of wristband. ", sep = "")
```

```{r print_loreal_4x, results="asis", echo=FALSE, eval=wristbands_time_adjusted_one_week_not_weight}
cat("The data is the raw nanograms found normalized to time-adjust the values as though the wristband were worn for exactly one week. ", sep = "")
```

```{r print_loreal_4x3, results="asis", echo=FALSE, eval=wristbands_week_and_weight_adjusted}
cat("The data shows the amount of each chemical in nanograms per gram of wristband, adjusted for the time worn to make results comparable.",
  sep = ""
)
```

```{r print_loreal_4x2, results="asis", echo=FALSE, eval=(wristbands_time_adjusted_one_day & FALSE) }
# NOTE:  I think i suppressed this message from ever showing BECAUSE i don't think it is necessary and adds complications to understanding

cat("The data is the raw nanograms found normalized to time-adjust the values as though the wristband were worn for exactly one day. ")
```

<!-- Values below the limit of detection are not included in the statistical analyses and are listed as zeros. -->

```{r StatSummary, results='asis', echo=FALSE, eval=TRUE, message=FALSE}
### Had error where i was renaming columns for 2nd time so it didn't work.
### Need to test if column names wrong and rename only if wrong:
if ("Chemical_Name" %in% colnames(statSummary)) {
  statSummary <- statSummary %>% dplyr::rename("Chemical Name" = Chemical_Name, 
                                               "Standard Deviation" = Standard_Deviation,
                                               "Smallest Value Found" = MinResult ,
                                               "Largest Value Found" = MaxResult,
                                               "Average Value Found" = MeanResult,
                                               "Middle Value Found" = MedianResult,
                                               "How Many Wristband Had this" = Count)
}


if (HideIndividualization) {
  panderOptions("big.mark", ",") # THIS line ADDS a COMMA in MOST of the numbers (not all... )

  pandoc.table(as.data.frame(statSummary),
    caption = "Statistical Report on all Chemicals on all Wristbands",
    justify = c("right", "right", "right", "right", "right", "right", "right"),
    emphasis.rownames = TRUE,
    split.table = Inf
  )
} else {
  #
  oneResultStatSummary <- oneResult %>%
    select(ParameterName, Result) %>%
    rename("Chemical Name" = ParameterName) %>%
    #right_join(statSummary, by = "Chemical Name") %>% ## THIS RIGHT JOIN makes it for EVERY chemical found anywhere...
    left_join(statSummary, by = "Chemical Name") %>% ## THIS left JOIN makes it for ONLY chemical found on this wristband
    replace_na(list(Result = 0)) %>%
    rename(!!paste(pureSubjectName, "Result", sep = " ") := Result)

  panderOptions("big.mark", ",") # THIS line ADDS a COMMA in MOST of the numbers (not all... )

  pandoc.table(as.data.frame(oneResultStatSummary),
    caption = paste("Statistical Report on all Chemicals on ", pureSubjectName, " wristband", sep = " "),
    justify = c("right", "right", "right", "right", "right", "right", "right", "right"),
    emphasis.rownames = TRUE,
    split.table = Inf
  )
  
  
  
  
}



if (FALSE) { # THIS IS THE BIG DATA

  panderOptions("big.mark", ",") # THIS line ADDS a COMMA in MOST of the numbers (not all... )

  pandoc.table(as.data.frame(bigStatSummary),
    caption = "Statistical Report on all Chemicals on all Wristbands found  in Large Demo Set compared to this smaller data set",
    justify = "right",
    emphasis.rownames = TRUE,
    split.table = Inf
  )
}


if (OutputBigComparisonStatTable) {
  panderOptions("big.mark", ",") # THIS line ADDS a COMMA in MOST of the numbers (not all... )

  pandoc.table(as.data.frame(bigStatSummaryJustTheseChemicals),
    caption = "Statistical Report on all Chemicals on This Groups Wristbands compared to values for these chemicals in Larger Demo  data set",
    justify = "right",
    emphasis.rownames = TRUE,
    split.table = Inf
  )
}





# =======
###
### THIS STUFF BELOW is the area that had some kinda conflict not sure what happened in GIT so i comment this out and leave stuff ABOVE for NOW
###
### IF I WANTED TO DO statSummaryand include e ONE user's chemical results in a list showing all chemicals found
# Then:  make the oneResultStatSummary and other pandoc table below...
#  oneResultStatSummary<- oneResult %>%
#    select(ParameterName,Result) %>%
#    rename(!!paste(subject,"Result",sep=" "):= Result) %>%
#    rename("Chemical Name"=ParameterName) %>%
#    right_join(statSummary,by="Chemical Name")
#
#  panderOptions("big.mark", ",") # THIS line ADDS a COMMA in MOST of the numbers (not all... )
#
#  pandoc.table(as.data.frame(oneResultStatSummary)
#               ,caption=paste("Statistical Report on all Chemicals on just",subject,"wristband",sep=" ")
#               ,justify=c("right","right","right","right","right","right","right","right")
#               ,emphasis.rownames=TRUE
#               ,split.table = Inf
#               )
# }
#>>>>>>> 88bf3a8b0c245ea66eeb8eddcecef7284980b12c
```

<br> <br>
