---
title: "New R Markdown Project"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    self_contained: true
    number_sections: true
    toc_depth: 3
    df_print: "paged"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This is the introduction section of your new R Markdown project. Describe the purpose and goals of this project here.

## Bootstrap Examples Using bsplus

### Modal Dialog Example
```{r modal_example, echo=FALSE}
library(bsplus)
library(htmltools)

# Creating a modal dialog with a button to open it
bs_modal(id = "exampleModal", title = "Modal Example", body = "This is a simple modal pop-up to display information.")

# Adding a button to trigger the modal
tags$button("Click Me", class = "btn btn-primary", `data-toggle` = "modal", `data-target` = "#exampleModal")
```

### Accordion Example
```{r accordion_example, echo=FALSE}
bs_accordion(id = "accordionExample") %>%
  bs_append(title = "Section 1", content = "This is the first section.") %>%
  bs_append(title = "Section 2", content = "This is the second section.")
```

### Tooltip Example
```{r tooltip_example, echo=FALSE}
# Adding a tooltip to a span element
tag_list <- tags$span("Hover over me", class = "tooltip-element", title = "This is a tooltip")
tag_list
```

### Popover Example
```{r popover_example, echo=FALSE}
# Adding a popover to a button
tags$button("More Info", class = "btn btn-info", `data-toggle` = "popover", `data-content` = "More detailed information in this popover.", title = "Popover Title")
```

### Collapsible Panel Example
```{r collapse_example, echo=FALSE}
# Creating a collapsible panel
tags$div(
  class = "card",
  tags$div(class = "card-header", "Show More"),
  tags$div(class = "collapse", id = "collapseExample", "This content is hidden until expanded.")
)
```

### Tabs Example
```{r tabs_example, echo=FALSE}
# Creating tabbed content
tags$div(
  class = "tab-content",
  tags$ul(
    class = "nav nav-tabs",
    tags$li(class = "nav-item", tags$a(class = "nav-link active", href = "#tab1", `data-toggle` = "tab", "Tab 1")),
    tags$li(class = "nav-item", tags$a(class = "nav-link", href = "#tab2", `data-toggle` = "tab", "Tab 2"))
  ),
  tags$div(class = "tab-pane active", id = "tab1", "Content for Tab 1"),
  tags$div(class = "tab-pane", id = "tab2", "Content for Tab 2")
)
```

## Data Preparation
```{r}
# Load necessary libraries
library(dplyr)

# Placeholder for data preparation code
```

## Analysis
```{r}
# Placeholder for analysis code
```

## Results
```{r}
# Placeholder for results
```

## Conclusion
Summarize your findings and future directions here.
