---
title: "Internal Link Demonstration"
output:
  
  pdf_document:
    toc: yes
    toc_depth: '3'
  rmdformats::readthedown:
    fig_height: 14
    fig_width: 10
    self_contained: true
    number_sections: true
    toc_depth: 3
    df_print: "paged"
  distill::distill_article:
    toc: true
    toc_depth: 4
  editor_options: 
    chunk_output_type: console
---

<!--               
output:
  html_document:
    fig_height: 14
    fig_width: 10
    self_contained: true
    mode: selfcontained
    theme: cerulean
    toc: true
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    df_print: "paged"
    keep_md: true
  pdf_document:
    toc: yes
    toc_depth: '3'
  distill::distill_article:
    toc: true
    toc_depth: 4
  editor_options: 
    chunk_output_type: console
  

-->


* Go to [tablex](#table)
* Go to [plot](#custom-idx)

```{r}
#| include = FALSE
library(dplyr)
library(ggplot2)
```

### Plotx {#custom-idx}

```{r plot-caption}
mtcars %>% 
  ggplot(aes(x = hp, y = mpg)) +
  geom_point()
```

### Table  {.tabset}

```{r}
mtcars %>% 
  glimpse()
```



#### a tab one
some text in a tab

some text in a tab
some text in a tab

some text in a tab
some text in a tab
some text in a tab

#### a tab two

Some more text
Some more text
Some more text
Some more text
Some more text
Some more text
Some more text



# Your Analysis Report

Some content here...

## Download the Full HTML File

<div style="text-align: center;">
  <button onclick="downloadHTML()">Download Full HTML</button>
</div>

<script>
function downloadHTML() {
  // Get the current HTML content as a Blob
  const blob = new Blob([document.documentElement.outerHTML], { type: 'text/html' });
  
  // Create a download link
  const link = document.createElement('a');
  link.href = URL.createObjectURL(blob);
  link.download = "YourReport.html";  // Name for the downloaded file
  
  // Trigger the download
  link.click();
  
  // Cleanup the URL object
  URL.revokeObjectURL(link.href);
}
</script>

## More Analysis

More content goes here...
