---
title: "reportOnPatchVsMasterParam"
output: html_document
date: "2024-11-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("TestingRandRMD","patchTestAnalysisVSotherTests.R"))

```

```{r set_variables, include=FALSE}

ac1000_compounds <-howManyCompoundsInTest("AC-1000")
f1000_compounds <- howManyCompoundsInTest("F-1000")
ac1000_and_f1000_compounds <- howManyCompoundsIn2Tests("AC-1000","F-1000")

ac1000_match <- howManyCompoundsMatchTest("AC-1000")
f1000_match <- howManyCompoundsMatchTest("F-1000")

ac1000_and_f1000_match <- howManyCompoundsMatch2Tests("AC-1000","F-1000")


```
## Patch Test Quicky Peek

Doing a quick analysis shows that there are `r ac1000_compounds` compounds in the "AC-1000" test.  There are `r f1000_compounds` compounds in the "F-1000" test.    
There are a total of `r ac1000_and_f1000_compounds` unique compounds between those two patch tests.

Our standard DRS MAS15 test captures `r ac1000_match` of the "AC-1000" compounds and captures `r f1000_match` of the "F-1000" compounds and 
`r ac1000_and_f1000_match` in total of the combined compounds.

The percentage coverage of the combined AC-1000 and F-1000 tests with our one MAS15 test is `r percent(ac1000_and_f1000_match/ac1000_and_f1000_compounds,0.1)`


```{r printResults1}

findMatchingRows(getPatchData("AC-1000"),masterParam) %>% gt()
findMatchingRows(masterParam,getPatchData("AC-1000")) %>% gt()

findMatchingRows(masterParam,getPatchData("B-1000")) %>% gt()

findMatchingRows(masterParam,getPatchData("C-1000")) %>% gt()
findMatchingRows(masterParam,getPatchData("F-1000")) %>% gt()
findMatchingRows(masterParam,getPatchData("MN-1000")) %>% gt()
findMatchingRows(masterParam,getPatchData("PG-1000")) %>% gt()
findMatchingRows(masterParam,getPatchData("PL-1000")) %>% gt()
findMatchingRows(masterParam,getPatchData("R-1000")) %>% gt()
findMatchingRows(masterParam,getPatchData("SH-1000")) %>% gt()

# IF we do AC and F, what value do other tests add

# intersect(
# findMatchingRows(getPatchData("AC-1000"),masterParam),
# findMatchingRows(masterParam,getPatchData("AC-1000")),
# 
# findMatchingRows(masterParam,getPatchData("B-1000")),
# 
# findMatchingRows(masterParam,getPatchData("C-1000")),
# findMatchingRows(masterParam,getPatchData("F-1000")),
# findMatchingRows(masterParam,getPatchData("MN-1000")), 
# findMatchingRows(masterParam,getPatchData("PG-1000")) ,
# findMatchingRows(masterParam,getPatchData("PL-1000")) ,
# findMatchingRows(masterParam,getPatchData("R-1000")) ,
# findMatchingRows(masterParam,getPatchData("SH-1000"))) %>% gt()






```
